Label object representation and manipulation with ITK

### 2007-10-17 article/Article.tex
fix number of new classes
darcs-hash:20071017121855-2fc9d-973d89bdf576c3c1e1ea580d14d673744eb89df7.gz
a few words about the new classes
darcs-hash:20071017130413-2fc9d-7937580424e1be5848eb56c083dfff058783c979.gz

Richard Beare has recently introduced a new filter to efficiently labelize the
connected component with ITK, and has also proposed to use the run-length
encoding used in that filter to implement some of the most useful binary
mathematical morphology operators: the opening by attribute.
Following that idea, and after have searched a way to use the ITK's spatial
objects for this task, a new set of classes have been developed to represent and
manipulate the label images and the objects within them in ITK.
Those new classes have been used to implement several label images
manipulation based on object attributes, as well as the binary and label specialization of
some mathematical morphology filters based on the morphological reconstruction. This contribution comes
with 57 new classes, and should greatly enhance the binary mathematical
morphology in ITK.

@@

  \item The objects can be relabel, with the {\em
RelabelLabelMapFilter} classes. The order of the label is dependant
of the value of the attribute. Again, the user can choose to have the objects
with the highest attribute value in the first labels, or to have the objects
with the lowest attribute values in the first labels.
\end{itemize}

>>>>

Richard Beare has recently introduced a new filter to efficiently labelize the
connected component with ITK, and has also proposed to use the run-length
encoding used in that filter to implement some of the most useful binary
mathematical morphology operators: the opening by attribute.
Following that idea, and after have searched a way to use the ITK's spatial
objects for this task, a new set of classes have been developed to represent and
manipulate the label images and the objects within them in ITK.
Those new classes have been used to implement several label images
manipulation based on object attributes, as well as the binary and label specialization of
some mathematical morphology filters based on the morphological reconstruction. This contribution comes
with 61 new classes, and should greatly enhance the binary mathematical
morphology in ITK.

@@

  \item The objects can be relabel, with the {\em
RelabelLabelMapFilter} classes. The order of the label is dependant
of the value of the attribute. Again, the user can choose to have the objects
with the highest attribute value in the first labels, or to have the objects
with the lowest attribute values in the first labels.

  \item The region covered by the {\em itk::LabelMap} can be changed with
{\em itk::ChangeRegionLabelMapFilter} and its subclasses ({\em itk::CropLabelMapFilter},
{\em itk::PadLabelMapFilter} and {\em RegionFromReferenceLabelMapFilter}).

\end{itemize}
